---
title: "Sample Vendor Portal eCOA QC"
output: 
  pdf_document:
    toc: TRUE
    toc_depth: 1
    number_sections: no
  fontsize: 8pt 
documentclass: article
classoption: 
  - landscape
  - a4paper
header-includes:
  - \usepackage{fancyhdr}
  - \usepackage{datetime}
  - \pagestyle{fancy}
  - \fancyhead{}
  - \renewcommand{\headrulewidth}{0pt}
  - \fancyhead[RO,RE]{}
  - \fancyfoot[LO,LE]{\mmddyydate{\today}\ - \currenttime}
  - \fancyfoot[RO,RE]{Generated with https://go.gene.com/ga39925datacheck}
  - \fancypagestyle{plain}{\pagestyle{fancy}}
---

```{r global option, include=FALSE}
knitr::opts_chunk$set(fig.width=10,
                      fig.height=8.5,
                      comment=NA,
                      echo = FALSE,
                      warning=FALSE,
                      message=FALSE)

library(stringr)
library(dplyr)
library(tidyr)
library(knitr)
```

\newpage
# Description of Variables

Variable names in CAPS are from the raw data, while variable names with mixed casing are derived from this application's data-check algorithm.

Variable Name | Description                                              | Excludes Bowel Prep & Endoscopy (+1)
--------------|----------------------------------------------------------|-----------------
USUBJID       |Unique subject identifier                          | NA
Date          |Date of clinical visit/start of visit window       | NA
Time          |Time of clinical visit/start of visit window       | NA
VISITNUM      |Clinical visit number label                        | NA
VISIT         |Clinical Visit type                                | NA
BwlPrepDt     |Bowel prep date (if available) for the previous visit window | NA
EndoDt        |Endoscopy date (if available) for the previous visit window | NA
DRYCMP1N      |Count of total diaries (1 stool + 1 rectal bleeding is counted as 1 entry) completed in visit window | NA
QSTESTCD      |Short code notation for test category  | NA
QSTEST        |Extended test category label | NA
QSSTRESC      |Test result (character) | NA
QSSTRESN      |Test result (numeric) | NA
StlDiaryTot   |Count of total stool frequency diaries completed, excluding bowel prep date range | Yes
StlSum        |Sum of the most (2 or )3 recent stool frequency diary entry scores | Yes
SFSSCR1N      |Sum of the most (2 or )3 recent stool frequency diary entry scores | Yes
StlAvg        |Average of the most (2 or )3 recent stool frequency diary entry scores | Yes
AVGSFS1N      |Average of the most (2 or )3 recent stool frequency diary entry scores | Yes
RbDiaryTot    |Count of total rectal bleeding diaries completed, excluding bowel prep date range | Yes
RbSum         |Sum of the most (2 or )3 recent rectal bleeding diary entry scores | Yes
RBSSCR1N      |Sum of the most (2 or )3 recent rectal bleeding diary entry scores | Yes
RbAvg         |Average of the most (2 or )3 recent rectal bleeding diary entry scores | Yes
AVGRBS1N      |Average of the most (2 or )3 recent rectal bleeding diary entry scores | Yes

\newpage
# Stool Frequency Average Score Miscalculations 
```{r sf tbl}

paste(nrow(getStlData()),"records found")
if(nrow(getStlData()) > 0){
  getStlData() %>%
    dplyr::select(-VISITNUM) %>%
    knitr::kable()
}
```

# Rectal Bleeding Average Score Miscalculations 
```{r rb tbl}
paste(nrow(getRbData()),"records found")
if(nrow(getRbData()) > 0){
  getRbData() %>%
    dplyr::select(-VISITNUM) %>%
    knitr::kable()
}
```

\newpage
# Randomized Screen Failure Subjects 
```{r scrnf tbl}
paste(nrow(getScrnFailRndData()),"records found")
if(nrow(getScrnFailRndData()) > 0){
  getScrnFailRndData() %>%
    knitr::kable()
}
```

\newpage
# Bowel Prep Date/Endoscopy Mismatches 
This table outputs all records found where the bowel prep date and endoscopy date entered do not make sense:  

* Record of either bowel prep date or endoscopy but not the other
* Bowel prep that takes place after endoscopy
* Bowel prep more than 1 day prior to endoscopy

```{r bwlendo}
paste(nrow(getBwlEndoData()),"records found")
if(nrow(getBwlEndoData()) > 0){
  getBwlEndoData() %>%
    knitr::kable()
}
```

\newpage
# Duplicate Date Diary Entries 
```{r dup}
paste(nrow(getDupData()),"records found")
if(nrow(getDupData()) > 0){
  getDupData() %>%
    knitr::kable()
}
```